Fitting Multifactorial Models of Differential Expression

### 2022-06-06 DGE_comparison.Rmd
Push site rendered version of DGE_comparison.html

---
title: "Fitting Multifactorial Models of Differential Expression"
author: "Sam Bogan"
csl: molecular-ecology.csl
output:
  html_document:
    toc: yes
    toc_depth: 3
  word_document:
    toc: yes
    toc_depth: '3'
  pdf_document: default
  github_document: default
bibliography: DGE_Comp.bib
---

@@

>>>>

---
title: "Fitting Multifactorial Models of Differential Expression"
author: "Samuel N Bogan"
bibliography: DGE_Comp.bib
---

@@

#References
